\section{Experiments}
\label{sec:experiments}
The \xcloud model was implemented in Java employing simjava \cite{SimJava} as the event driven framework.

\subsection{\Ue, mobility and network}
To reveal the effect of varying load on the \dcs{}, the number of \ue{} service subscribers $N_{\ue}$, placement of the \dcs{}, and the number for services were varied independently throughout as many simulation scenarios.

%Additionally, for each run of $N_{ue}$ the number of services $N_{ser}$ and the placement of the \dcs{} was varied. 
In proportion to the range of movement and to be evenly divisible by $N_{dc}^2$, the simulation domain spans 16 \rbss{} $N_{rbs}$. The cell dimension $d_{rbs}$ adhere to a proposed maximum cell radius of 750 m, as detailed in \cite{shahab2013framework}. Although rectangular, its area equates to the area of a circular cell with a radius of 750 m, which results in a cell width and hight $d_{rbs}$ of 1300 m. The population of \ues{} subscribing to a service $N_{ue}$ ranged from from 10 to 1600 \ues{}, doubling with each increment. The number of \dcs{} $N_{dc}$ was varied between 16, 4 and 1, with each \dc{} serving 1, 4 or 16 \rbss{} respectively. Additionally, for each run of $N_{ue}$ the number of services $N_{ser}$ was varied between 1 and 5.
%The network spans 9 radio access nodes, $N_{rbs}$.

The simulation time is set to 8 hours, $T_{sim}=28800$ seconds, leaving sufficient time for each \ue{} to on average visit half of the \rbss{}.

\subsection{\Dc{}, VM, and application parameters}
Times for resource allocation and release and log normal distributed with means $T_{vm\_init}$ and $T_{vm\_release}$ respectively, and are modelled after Amazon EC2 measurements for m1.small instance (1~vCPU, 1.7 GB of RAM and 160 GB disk) \cite{5719609}. %http://aws.amazon.com/ec2/previous-generation/

The service time for each application is set heterogeneously, proportional %to the mean request generation rate over the number of \rbss{} and the number of VMs running, see Equations \ref{eq:service_rate} \& \ref{eq:service_time}. Where $\lambda_{sys}$ is the aggregate arrival rate to the system, and $K$ is a scaling factor set to 1. Each VM is provisioned to handle 20 concurrent active subscribers ($N_{\ue} = 20$). The mean service time for each VM is thus $1/\mu$.

%\begin{equation}
%	\label{eq:service_rate}
%	\mu = K \cdot  \lambda_{ue} \cdot N_{ue} \cdot \frac{ N_{services}}{N_{dc}} 
%\end{equation}
%
%\begin{equation}
%	\label{eq:service_time}
%	\lambda_{ue} = \frac{ \bar{N}_{requests} }{\bar{N}_{requests} \cdot \bar{T}_{request} + \bar{T}_{session} }
%\end{equation}

As resources are assumed to be ubiquitous we wish to observe the effects of an overloaded \dc{}. For modelling simplicity, \dc{} capacity if constrained by a limit of how many VMs $N_{vm,limit}$ it simultaneously can host. Our experiment regards two fundamental provisioning scenarios. When the VM limit $N_{vm,limit}$ has been reached, either any new VMs are denied or the additionally needed \dc{} capacity is shared equally amongst the $N_{i,vm}$ VMs by increasing the service time $T_{i,ser}$ with a factor $K_{over}$, see Equation \ref{eq:shared_service_time}.

\begin{equation}
	\label{eq:shared_service_time}
	K_{over} = \frac{ \max(N_{i,vm},N_{vm,limit}) }{ N_{vm,limit} }
\end{equation}

%\subsection{VM migration schemes}
%For each scenarios the simulation reveals how often the service resides in each \dc{}, how many times one service is started and stopped in each \dc{}, and how how much service latency is incurred by starting and stopping a service throughout the simulation.

%The \dc{} service time for the ith \dc{} $T_{i,vm}$ is set proportional to the mean request generation rate over the number of \rbss{}, and the number of VMs running on the ith \dc{} $N_{i,vm}$, see Equation \ref{eq:service_time}.

Simulation model parameters used in the experiments can be found in Table~\ref{table:simulation_parameters}, likewise the service parameters are declared in Table~\ref{table:traffic_parameters}.


%where $i$, $j$, $vm$, $K$, $N_{ser}$, $\bar{\lambda}_{sys}$, $N_{rbs}$. 

\begin{table}[tb]
 	\centering
 	
    \begin{tabular}{|l|l|} \hline
    	\textbf{Parameter}    	& \textbf{Value}			\\ \hline
    	$N_{ue}$						& 10--500 (step: 10)	\\ \hline
    	$N_{rbs}$						& 16								\\ \hline
    	$N_{dc}$						& $\{1,4,16\}$				\\ \hline
    	$N_{ser}$						& 1--5							\\ \hline
    	$T_{ser}$						& \\ \hline
    	$T_{sim}$						& 28800 seconds\\ \hline
    	$d_{rbs}$						& \\ \hline
    	$T_{net}$						& \\ \hline
        $N_{vm,limit}$                  & \\ \hline
        %$T_{sus}$						& \\ \hline
        %$N_{i,sus vm}$				& \\ \hline
        $T_{vm\_init}$				& avg 82 s, min 69 s, max 126 s \\ \hline
        $T_{vm\_release}$		& avg 21 s, min 18 s, max 23 s \\ \hline
        $T_{vm\_transfer}$		& \\ \hline
		$D_{vm\_transfer}$		& \\ \hline
		$T_{vm\_downtime}$	& \\ \hline
		$D_{memory\_pull}$	& \\ \hline
		$N_{memory\_pull}$	& \\ \hline
    \end{tabular}
    
    \caption{Simulation parameter values}
    \label{table:simulation_parameters}
\end{table}

\begin{table}[tb]
	\centering
	
    \begin{tabular}{|l|l|l|}\hline
    	\textbf{Component}  	& \textbf{Distribution} 	& \textbf{Parameters}     \\ \hline
    	$S_f$   & Pareto   				    & K=133000 $\alpha$ =1.1  \\ \hline
    	$S_r$   & Pareto    				& K=1000         \\ \hline
    	$D_r$ 	& Weibull    				& $\alpha$ =1.46 $\beta$ =0.382 \\ \hline
    	$D_s$ 	& Pareto     				& K=1 $\alpha$=1.5      \\ \hline
    \end{tabular}
    
%Session arrival,Poisson process (0.0005≤λ≤0.01),,
%Number of clicks,Inverse Gaussian (μ=5; λ=3),5,1.28
%Inter-click idle time (s),Lognormal (m=3; σ=1.1),36.8,56.4

    \caption{Service model components}
    \label{table:traffic_parameters}
\end{table}

\subsection{Measurements}
To ensure statistical accuracy, each simulation scenario was independently replicated 10 times.

For each above mentioned simulation scenario, every request is recorded with where it was processed, if it was terminated, the time spent queuing, processing, and propagating. Similarly, for each VM the proportion of time spent in each state is recorded.